---
title: "Artifacts & reproducibility"
description: "A read-only publication manifest: saved evidence, source paths, hashes, and explicit provenance gaps."
---

## What gets reproduced

`site/scripts/render-artifacts.R` reads the existing nine parquet files below
and creates two charts, article tables, and the shared provenance footer under
`site/_generated/`. `site/scripts/render-matchup.R` separately reads the processed
football checkpoints returned by `explain_matchup()` and creates one retrospective
case-study chart, tables, narrative, and a page-specific manifest. Quarto renders
only the five named pages into `site/_site/`.
No pipeline/model source is executed, and nothing is written into `data/`,
`outputs/`, or draft state.

**Public-safe replacement:** the historical NotebookLM corpus, CLV summaries,
and matchup exports are deliberately excluded. Deploy only `site/_site/`, never
the repository root or the historic outputs directory.

## Evidence map

| Artifact | Role |
|---|---|
| `data/05_backtests/38_market_efficiency.parquet` | Four efficiency-test estimates/SEs/nulls; also contains strategy-summary rows, excluded from the coefficient chart. |
| `data/05_backtests/38_strategy_summary.parquet` | Aggregate ROI and count for all six strategies. |
| `data/05_backtests/38_strategy_by_season.parquet` | Season coverage and context: aggregate losses do not mean every season lost. |
| `data/05_backtests/38_bets.parquet` | Strategy threshold units, evaluation seasons, and independent recomputation of summary ROI. Rows repeat games across strategies. |
| `data/04_models/36_incremental_value.parquet` | Paired-bootstrap Brier deltas and intervals. |
| `data/04_models/36_model_metrics.parquet` | Raw and Platt-calibrated performance; a separate experiment from the power-index backtest. |
| `data/04_models/36_predictions.parquet` | Test-season coverage and game-level predictions, repeated across model blocks and overlapping splits. |
| `data/04_models/36_calibration.parquet` | Saved calibration-bin context; not a standalone proof of calibration. |
| `data/04_models/36_feature_importance.parquet` | Feature-gain context, not causal or incremental-value evidence. |

Paths are repository-relative identifiers, **not download links**. Raw artifacts
are intentionally not bundled. A fresh clone needs the reviewed saved artifacts
supplied separately; this render fails if they are missing. No fallback uses
fabricated, stale-text, or demo data.

## Historical matchup snapshot

The matchup walkthrough calls `explain_matchup("PHI", "DAL", 2024, week = 10)`
against the existing processed checkpoints. It supplies an empty temporary
`outputs_dir`, so no market or opening-line field can enter the public snapshot.
The generated page-specific manifest fingerprints every processed RDS checkpoint
and the source/helper code used. Its mixed time boundary—full-season team metrics
plus Week 10 quarterback and injury context—is stated in the page, chart caption,
and manifest.

## Local commands

From the repository root, with Quarto, R, and `arrow`, `ggplot2`, `knitr`, and
`digest` available:

```sh
Rscript site/scripts/check-helper.R
quarto render site
python3 site/scripts/check-site.py
git diff --check
quarto preview site --no-browser
```

The full render automatically invokes the artifact-only helper. `renv.lock` is
an upstream environment manifest, not an activated project library. No package
installation, artifact regeneration, or lockfile changes occur during rendering.

## How to read the provenance

The shared footer records this publication's UTC generation time, current Git
HEAD, working-tree status, source artifacts, and separate data ranges. It does
not claim the saved model files were created by that commit or at render time.
The efficiency summary has no season column: its 2021–2025 range is the reviewed
scope documented in `AGENTS.md` and the producer, not something inferred from
the shorter bet ledger. Artifact hashes identify the exact bytes read.
Publication-source hashes distinguish uncommitted site edits from HEAD.

A fail-closed editorial guard stops rendering if the saved evidence no longer
supports this article's negative-strategy / unresolved-schematic conclusions.
This guards the **publication**, not the research pipeline: new evidence must
prompt an editorial review rather than a model change to force old conclusions.

```{r}
#| echo: false
#| results: asis
cat(readLines("_generated/manifest.qmd"), sep = "\n")
```

```{r}
#| echo: false
#| results: asis
cat(readLines("_generated/source-manifest.qmd"), sep = "\n")
```

[Methodology and limitations](methodology.qmd) · [Project overview](index.qmd)
